Maximum Entropy Spectral Analysis: a case study

### 2021-03-25 paper/mesa.tex
Draft for the conclusions

Turning to the comparison between MESA and Welch's method, we find that the PSD estimation provided by the Welch's method is more noisy (i.e. has a large number of spurious peaks) rather than PSD provided by MESA. The different behavior is more manifest in the low frequency sector.
The result does not change much by changing the hyperparameters required for Welch algorithm.
\sschmidt{Other observations??}

@@

\section{Final remarks and future prospects} \label{sec:conclusion}
\blindtext
\blindtext
\blindtext

\sschimidt{Is it fine to ackonowledge people helping with temperature data and seismic data?}
	\begin{acknowledgments}
%S.S. wants to thank Maurizio Maugeri and Costanza Rossi for useful discussions.

>>>>

Turning to the comparison between MESA and Welch's method, we find that the PSD estimation provided by the Welch's method is more noisy (i.e. has a large number of spurious peaks) rather than PSD provided by MESA. The different behavior is more manifest in the low frequency sector.
The result does not change much by changing the hyperparameters required for Welch algorithm.
\sschmidt{Elaborate a bit more on this... Right now it is a very poor comment (blame is on me!)}

@@

\section{Final remarks and future prospects} \label{sec:conclusion}

We presented a case study of the application of Maximum Entropy principle in the realm of spectral estimation: it provides a closed form estimation of the power spectral density, bridging the spectral analysis with the study of autoregressive processes. The method has the towfold advantage of avoiding any unjustified assumption on the observed time series and of providing a simple context for forecasting the time series. We provided a ready to use python code, called `memspectrum' and we performed numerical studies of its performance.
We investigated the use of different loss functions for the purpose of correctly estimating the autoregressive order for the estimation and we found that different loss functions are required for different situations.
Finally, we performed a comparison between PSDs computed with MESA and standard Welch's algorithm and we applied our method to several time series of interest in physics.

As outlined in sec.~\ref{sec:Welch_comparison}, the MESA provides PSD estimates with less noise than the standard Welch algorithm, thus making it a good alternative for it. The use of MESA is particularly useful for short time series samples, where Welch method is outperformed in accuracy and conficence.
It has to be said that our method can be quite computationally expensive, as compared to standard Welch's algorithm. However, for short time series, the computational cost is still managable.

Besides providing an alternative to standard methods of spectral estimate, MESA opens up several oppurtunities in the context of time series analysis.

First of all, as short time series are required to produce meaningful PSD estimations, it can be suitable in the context of PE...
\textbf{##############PE part here#############}

Furthermore, MESA provides a simple, but robust and quite accurate, predictor for the time series. This fact is remarkable and can be used in time series analysis for several purposes.
As already discussed in sec~\ref{sec:LIGO_forecasting}, an anomaly detection pipeline can be easily built using the forecasts of MESA: the predictions can form a baseline to compare the actual observations with. Whenever the observed data are outside the expectations, an anomaly detection can be claimed.
Of course such predictions can be done with a more accurate (perhaps nonlinear model); however MESA has the advantage of being simple and fast to train, while providing good (short term) predictions.

\sschmidt{Other stuff with forecasting?}

We believe that Maximum Entropy Spectral Analysis, despite being an ``old" theory, has still the potential to become the standard in future time series analysis, due to its theorical elegance and to its reliable performance in a vast range of application.

	\begin{acknowledgments}
%We want to thank Maurizio Maugeri and Costanza Rossi for useful discussions.
\sschmidt{Is it fine to ackonowledge people helping with temperature data and seismic data?}
